The title

### 2016-10-18 analysis/paper/paper.Rmd
description cuttings

>>>>

In general, the cutting consist of 4 layers and a thin soil profile of about 5 cm. The uppermost layer is made from brownish red poorly sorted gravel that contains medium to well-rounded cobbles and pebbles. The slightly silty sandy matrix contains an increasing amount of gravel towards the top. The cobbles are weathered and the larger ones are made from fossil wood. There is no bedding, sorting or imbrication visible. Fine roots penetrate the profile throughout. The lower contact with the following layer is moderately sharp. The gravel layer is followed by a brownish red silty sand that is well rounded with no obvious bedding. There occasional lighter patches that could indicate decayed pebbles. The contact with the next layer is fairly sharp. Between the bedrock and the red sand layer there is angular weathered bedrock intertwined with a dark band, possibly either a weathered palaeosurface or a weathered intrusion of host rock. The bedrock itself is medium to fine-grained light grey and brown red sand including some silt. The red band could be filling from above. A few isolated roots are visible.
